\paperTitle

### 2014-05-18 doc/icml2014/undirected.tex
Minor change in phi notation - undirected

Let $\phi_{a,\sN(a)}(a, \sN(a)) = \sum_{\sC \ni a} \phi_\sC(\bx_\sC,\bh_\sC)$
denote the sum over cliques $\sC$ that contain $a$; note that $\phi_{a, \sN(a)}$ only depends on $a$ and its neighbors $\sN(a)$.
We can write each conditional log-likelihood from \equationref{pseudolikelihood} as:
\begin{align*}
p_\theta(a \mid \sN(a)) = \exp(\theta^\top\phi_{a,\sN(a)}(a, \sN(a)) - A_a(\theta; \sN(a))),
\end{align*}
where the conditional log-partition function $A_a(\theta; \sN(a)) = \log \sum_{a'} \exp(\theta^\top\phi_{a,\sN(a)}(a', \sN(a)))$
involves marginalizing only over the single variable $a$.

>>>>

Let $\phi_{a,\sN(a)}(a, \sN(a)) = \sum_{\sC \ni a} \phi_\sC(\bx_\sC,\bh_\sC)$
denote the sum over cliques $\sC$ that contain $a$; note that $\phi_{a, \sN(a)}$ only depends on $a$ and its neighbors $\sN(a)$.
We can write each conditional log-likelihood from \equationref{pseudolikelihood} as:
\begin{align*}
p_\theta(a \mid \sN(a)) = \exp(\theta^\top\phi_{a,\sN(a)}(a, \sN(a)) - A_a(\theta; \sN(a))),
\end{align*}
where the conditional log-partition function $A_a(\theta; \sN(a)) = \log \sum_{\alpha \in [k]} \exp(\theta^\top\phi_{a,\sN(a)}(\alpha, \sN(a)))$
involves marginalizing only over the single variable $a$.
